Tensor anisotropy as a tracer of cosmic voids

### 2015-02-16 cosmic_voids.tex
conclusiones al 80%

Our results extend the evidence for a universal density profile down
to smaller sizes as the one probed by \cite{Hamaus14}.

>>>>

The velocity profiles show the expected correlation with the features
already observed in the density, most notably the radial velocity is
cero close to flat regions in the density profile and positive around
regions of increasing density with radius.

The Fractional Anisotropy profiles also show remarkable similarities,
(inside each class of subcompensated and overcompensated)
and a close correlation with the behaviour in the density and velocity
profiles. 
From these profiles it becomes clear that our choice to delimit an
overcompensated void coincides with a ridge in the fractional
anisotropy. For the subcompensated voids the void boundary is located
for regions with an average FA value of $\sim 0.7-0.8$.

Put together, the results for the radial profiles support the 
evidence for a universal density profile using smaller void sizes
than the ones probed by \cite{Hamaus14}.
